Classical Planning Algorithms ¡ on the Atari Video Games

### 2014-11-19 icaps15-paper/paper.tex
Corrected sentence in Experimental Section

Likewise, in \Freeway\ and \Berzerk\ both $\IW(1)$ and \BFS\ attain a better
score than the baseline semi-random algorithm \emph{Perturb} in
\cite{bellemare:jair2013}, that beats \UCT\ on those games.
%% to say the 2 lines below must add context: .. eg
%%% ``which in *these games* outperforms both \UCT\ and the reinforcement learning methods.''
%% add it if that's the case ..
\emph{Perturb} is a simple algorithm
that selects  a fixed  action with probability $0.95$, and a random
action with probability $0.05$.  For \emph{Perturb}, BNVB do not report 
the average score  but the  best score.  \emph{Perturb} manages to do well in domains where rewards
are deep but can be reached by  repeating the same action.
This is the case of \Freeway, where a chicken has to run across a ten lane
highway filled with traffic. Every time the chicken gets across, there is one
unit of reward. If the chicken is hit by a car, it has to start again. 
In \Freeway, only $12$ out of $18$ possible actions have an effect:
$6$ actions in moving the chicken up one lane (up-right, up-left, up-fire, up-right-fire, up-left-fire), 
$6$ in moving the chicken down one lane (down-right, down-left, down-fire, down-right-fire, down-left-fire), 
and $6$ actions do nothing.  \emph{Perturb}  does well in this domain 
when the selected fixed action is one of the $6$ that moves the chicken up.  As noted 
in Table~\ref{performance} and seen in the provided video, \UCT\ does not manage to take the chicken
across the highway at all. The reason for \UCT\ to perform erratically 
is that the roll-outs do not manage to collect any reward. A sequence of actions 
with at least $10$ actions embedded that move the chicken up are required in order 
to collect a reward. Since the probability for the roll-out to do an action that moves the chicken up 
is $1/3$, the likelihood of \UCT\ generating such a sequence of actions with the parameters chosen
by BNVB is rather low.
%% the previous number was not correct; no-op actions do not count, and thus needs
%%% 200 more move up actions than move down actions, although this is not accurate either
%%%% as move down actions that take chicken below the screen count as no-ops too ..
$\IW(1)$ does not have this limitation and is best in \Freeway.

>>>>

Likewise, in \Freeway\ and \Berzerk\ both $\IW(1)$ and \BFS\ attain a better
score than the baseline semi-random algorithm \emph{Perturb} in
\cite{bellemare:jair2013}, that beats \UCT\ on those games.
%% to say the 2 lines below must add context: .. eg
%%% ``which in *these games* outperforms both \UCT\ and the reinforcement learning methods.''
%% add it if that's the case ..
\emph{Perturb} is a simple algorithm
that selects  a fixed  action with probability $0.95$, and a random
action with probability $0.05$.  For \emph{Perturb}, BNVB do not report 
the average score  but the  best score.  \emph{Perturb} manages to do well in domains where rewards
are deep but can be reached by  repeating the same action.
This is the case of \Freeway, where a chicken has to run across a ten lane
highway filled with traffic. Every time the chicken gets across, there is one
unit of reward. If the chicken is hit by a car, it has to start again. 
In \Freeway, only $12$ out of $18$ possible actions have an effect:
$6$ actions in moving the chicken up one lane (up-right, up-left, up-fire, up-right-fire, up-left-fire), 
$6$ in moving the chicken down one lane (down-right, down-left, down-fire, down-right-fire, down-left-fire), 
and $6$ actions do nothing.  \emph{Perturb}  does well in this domain 
when the selected fixed action is one of the $6$ that moves the chicken up.  As noted 
in Table~\ref{performance} and seen in the provided video, \UCT\ does not manage to take the chicken
across the highway at all. The reason for \UCT\ to perform erratically 
is that the roll-outs do not manage to collect any reward. A sequence of actions 
with at least $10$ actions embedded that move the chicken up are required in order 
to collect a reward. Since the probability for the roll-out to choose an action that moves the chicken up 
is $1/3$, with the parameters chosen by BNVB, the likelihood of \UCT\ generating such a sequence of actions 
that \emph{also} avoids incoming traffic in a timely fashion is rather low.
%% the previous number was not correct; no-op actions do not count, and thus needs
%%% 200 more move up actions than move down actions, although this is not accurate either
%%%% as move down actions that take chicken below the screen count as no-ops too ..
$\IW(1)$ does not have this limitation and is best in \Freeway.
